---
title: "Conversion of Meteorological .nc to Pecan Format"
output: html_document
---


### TODO
- Compare `clm_version.nc` to `pecan_version_example.nc`
- Change column/header names to match
- Rescale values by 10? 

#### Comparison of variable names and units between two files

Pecan var name    | Pecan var unit  | CLM var name | CLM var unit    | convert name? | convert unit?
----------------- | --------------- | ------------ | ------------    | ------------- | -------------
longitude         | degrees_east    | LONGXY       | degrees E       | Y             | N?
latitude          | degrees_north   | LATIXY       | degrees N       | Y             | N?
time              | days since 1700 | time         | days since 2000 | N             | Y
air_temperature   | K               | TBOT         | K               | ?             | N
relative_humidity | %               | RH           | %               | Y             | N
specific_humidity | kg kg-1         |              |                 |               |
surface_downwell  | W m-2           | FSDS         | W/m2            | Y             | N?

#### Explore CLM version met file

```{r}
library(ncdf4)

clm_met <- nc_open("clm_version.nc")
print(clm_met)

clm_lati_var <- ncvar_get(clm_met, "LATIXY")
clm_long_var <- ncvar_get(clm_met, "LONGXY")
clm_time_var <- ncvar_get(clm_met, "time") 
clm_temp_var <- ncvar_get(clm_met, "TBOT")
clm_solar_var <- ncvar_get(clm_met, "FSDS")
```

#### Explore CLM version met file

```{r}
pecan_met_ex <- nc_open("pecan_version_example.nc")
print(pecan_met_ex)

pecan_lati_var <- ncvar_get(pecan_met_ex, "latitude")
pecan_long_var <- ncvar_get(pecan_met_ex, "longitude")
pecan_time_var <- ncvar_get(pecan_met_ex, "time")
pecan_temp_var <- ncvar_get(pecan_met_ex, "air_temperature")
pecan_solar_var <- ncvar_get(pecan_met_ex, "surface_downwelling_shortwave_flux_in_air")
```

#### Met file structure comparison

Both have weather data for single location (one lat-lon coordinate) and time range is a year, though Pecan file has values recorded 3x as often. 

Solar/flux has very different values. CLM is 0-200 while Pecan is 10e36. Does latter need to be converted because of decimals? 
